Profile likelihoods for geostatsistical models using GPU's

### 2022-01-09 pkg/oldgpuRandom/inst/doc/L2021_11/paper2.Rnw
paper2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3105 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<swisssummarycompare, echo=FALSE>>=
table1 <- read.csv("Book1.csv")
colnames(table1) <- c('Parameter','Estimate','95% CI', 'Estimate','95% CI')
knitr::kable(table1, format = "latex", align = c("rcccc"),booktabs = T, linesep = "", caption= "Summary comparison", digits=3)%>%
 kable_styling(full_width = FALSE, position = "center", latex_options = "HOLD_position") %>%
 add_header_above(c(" ", "geostatsp" = 2, "gpuBatchMatrix" = 2)) 
@

<<swiss_profile_many,echo = FALSE, eval=TRUE, cache=TRUE, fig.width=4,fig.height=3, fig.show ="hold", fig.align='center', fig.cap = "profile LogL of slope parameter", out.width = "50%",dev='pdf',fig.pos="H">>=
setwd("/home/ruoyong/diseasemapping/pkg/oldgpuRandom/inst/doc/L2021_11")
knitr::include_graphics(c('profile_logl_swiss.png'))
@

<<swiss_profile_sole_prep, out.width = "100%", fig.align = "center",echo=FALSE>>=
knitr::include_graphics(c('swiss_pro_4.png'))
@

>>>>

<<swisssummarycompare, echo=FALSE>>=
table1 <- read.csv("Book1.csv")
colnames(table1) <- c('Parameter','Estimate','90% CI', 'Estimate','90% CI')
knitr::kable(table1, format = "latex", align = c("rcccc"),booktabs = T, linesep = "", caption= "Summary comparison", digits=3)%>%
 kable_styling(full_width = FALSE, position = "center", latex_options = "HOLD_position") %>%
 add_header_above(c(" ", "geostatsp" = 2, "gpuBatchMatrix" = 2)) 
@

<<swiss_profile_many,echo = FALSE, eval=TRUE, cache=TRUE, fig.width=4,fig.height=3, fig.show ="hold", fig.align='center', fig.cap = "profile LogL of slope parameter", out.width = "50%",dev='pdf',fig.pos="H">>=
setwd("/home/ruoyong/diseasemapping/pkg/oldgpuRandom/inst/doc/L2021_11")
knitr::include_graphics(c('profile_logl_swiss.png','betaprofile.png'))
@

<<swiss_profile_sole_prep, out.width = "50%", fig.align = "center",fig.pos="H",echo=FALSE>>=
knitr::include_graphics(c('swiss_pro_4.png','swiss_pro_2.png'))
@
